Considering scale in multilayer animal social networks

### 2020-06-21 paper/manuscript.Rmd
social distance

We generated multilayer networks across a series of social distance thresholds 
that relate to behavioural interactions that could occur within those distances
<!-- JWT: or something like that needs to be in the first sentence to relate the spatial distance to social scale upfront -->
for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and foraging) for the entire study period. At
the finest scale, individuals within 5 m of one another were considered in the
same group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. We calculated graph strength and
multidegree for each habitat layer and social distance threshold, and edge
<!-- JWT: can we call spatial distance social distance? -->
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial distance
threshold.

@@

>>>>

We generated multilayer networks across a series of social distance thresholds 
for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and foraging) for the entire study period. At
the finest scale, individuals within 5 m of one another were considered in the
same group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. Increasing social distance threshold 
is a proxy for potential behavioural interactions that occur across these distances.
We calculated graph strength and
multidegree for each habitat layer and social distance threshold, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial distance
threshold.

@@

<!-- TODO: somewhere ref:ml -->
